### 2017-06-09 sheets/talk-6/sheet-6.tex
Sheet 6: More minor edits

  Let $z$ be a greatest lower bound of the family $(x_i)_{i\in I}$. We show that $z$ is a product of $(x_i)_{i\in I}$.
  \begin{proof}
    We first have to define a family of maps $\Bigl(z \toby{p_i} x_i\Bigr)_{i \in I}$.
    This is trivial since we have $\forall i \in I: z \le x_i$.
    Now let $a \in A$ be an object and let $\Bigl(a \toby{f_i} x_i\Bigr)_{i \in I}$ be a family of maps from $a$.
    The existing of this maps means that $a$ is a upper bound of $(x_i)_{i\in I}$.
    Now by definition of least upper bound, $a \le z$, thus we have a arrow $\bar{f} \from a \to z$.
    All arrows are unique, thus $\bar{f}$ is unique and the diagram commutes. \qedhere
  \end{proof}
\end{answer}

@@

\begin{answer}
  \begin{proof}
    We first define the projection functions $p_1 \from V \oplus W \to V, p_2 \from V \oplus W \to W$:
    \begin{alignat*}{1}
      p_1(x,y) &:= x \\
      p_2(x,y) &:= y
    \end{alignat*}
    Now let $A$ be a vector space and $f_1 \from A \to V, f_2 \from A \to W$ be linear functions.
    We define $\bar{f}(a) := (f_1(a), f_(2))$. We clearly have
    \begin{alignat*}{2}
      p_1(\bar{f}(a)) &= p_1(f_1(a), f_2(a)) = f_1(a) \\
      p_2(\bar{f}(a)) &= p_2(f_1(a), f_2(a)) = f_2(a).
    \end{alignat*}
    Thus the diagram
    \[ \xymatrix{
        & A \ar[ldd]_{f_1} \ar@{.>}[d]|{\bar{f}\vphantom{\bar{\bar{f}}}} \ar[rdd]^{f_2} & \\
        & {V \oplus W} \ar[ld]^{p_1} \ar[rd]_{p_2} & \\
        V & & W
    } \]
    commutes. Now we have to show that $\bar{f}$ is the only map such that the above diagram commutes.
    Let $\tilde{f} \from A \to V \oplus W$ be a map such that $p_1 \of \tilde{f} = f_1 \land p_2 \of \tilde{f} = f_2$.
    \[
      \tilde{f}(a) = \bigl(p_1(\tilde{f}(a)), p_2(\tilde{f}(a))\bigr) = \bigl(f_1(a), f_2(A)\bigr) = \bigl(p_1(\bar{f}(a)), p_2(\bar{f}(a))\bigr) = \bar{f}(a)\qedhere
    \]
  \end{proof}
\end{answer}

@@

\begin{answer}
  \begin{proof}
    Let $i \from core(s-t) \to X$ be a inclusion function. Let
    $\xymatrix{
      A \ar[r]^f & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
    }$
    be a commuting diagram. Note that $f A \subseteq core(s-t)$.
    Thus we can define $\bar{f} \from A \to core(s-t)$ with $\bar{f}(a) := f(a)$.
    We see that $\forall a \in A: i(\bar{f}(a))=\bar{f}(a)=f(a)$, thus $i \of \bar{f} = f$.
    Let $\tilde{f} \from A \to core(s-t)$ be another map such that $i \of \tilde{f} = f$.
    Now $\tilde{f}(a) = i(\tilde{f}(a)) = i(\bar{f}(a)) = \bar{f}(a)$.
  \end{proof}
\end{answer}

@@

    \begin{itemize}
      \item[``$\Rightarrow$'']
        Let $s=t$. Then the fork
        $\xymatrix{
          X \ar[r]^{1_X} & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
        }$
        $1_X$ is an isomorphism.
        Let
        $\xymatrix{
          A \ar[r]^f & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
        }$
        be a fork.
        Clearly $\bar{f} := f$ is the only map $\bar{f} \from A \to X$ such that the diagram
        \[ \xymatrix{
          A \ar[rd]^f \ar@{.>}[dd]|{\bar{f}} & & \\
          & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y \\
          X \ar[ru]_{1_X} & &
        } \]
        commutes.
      \item[``$\Leftarrow$'']
        Let
        $\xymatrix{
          E \ar[r]^i & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
        }$
        be the equalizer and $i$ a isomorphism. Then by commutativity we get:
        \begin{alignat*}{4}
          && s \of i &= t \of i \\
          \Rightarrow  &\qquad& s \of i \of i^{-1} &= t \of i \of i^{-1} \\
          \Rightarrow  &      & s &= t
        \end{alignat*}\qedhere
    \end{itemize}
  \end{proof}
\end{answer}

@@

\begin{answer}
  \begin{proof}
    We show that $S := P$ is the coproduct of $X$ and $Y$ together with the projection functions $p_1$ and $p_2$.
    First note that because $Z$ is initial $s$ and $t$ are unique maps.
    Let
    $ \xymatrix{
      X \ar[r]^{f_1} & A & Y \ar[l]_{f_2}
    } $
    be a diagram in $\cat{A}$.
    We have to show that there is a unique map $\bar{f}' \from P \to A$ such that
    \[ \xymatrix{
      X \ar[rdd]_{f_1}\ar[rd]^{p_1} & & Y \ar[ldd]^{f_2} \ar[ld]_{p_2} \\
      & P \ar@{.>}[d]|{\bar{f}'} & \\
      & A &
    } \]
    commutes. We know that the diagram
    \[ \xymatrix{
      Z \ar[r]_s \ar[d]^t & X \ar[d]_{f_1} \\
      Y \ar[r]^{f_2} & A
    } \]
    commutes because $Z$ is initial.
    Now because this square is then a pushout square there exists a unique map $\bar{f}\from P \to A$ such that
    \[ \xymatrix{
      Z \ar[r]_s \ar[d]^t & X \ar[d]_{p_1} \ar[ddr]^{f_1} & \\
      Y \ar[r]^{p_2} \ar[drr]_{f_2}& P \ar@{.>}[dr]|{\bar{f}} & \\
      & & A  \\
    } \]
    commutes. We see that we can choose $\bar{f}' := \bar{f}$.
    Suppose we have another $\tilde{f} \from P \to A$ such that
    \[ \xymatrix{
      X \ar[rdd]_{f_1}\ar[rd]^{p_1} & & Y \ar[ldd]^{f_2} \ar[ld]_{p_2} \\
      & P \ar@{.>}[d]|{\tilde{f}} & \\
      & A &
    } \]
    commutes. Then
    \[ \xymatrix{
      Z \ar[r]_s \ar[d]^t & X \ar[d]_{p_1} \ar[ddr]^{f_1} & \\
      Y \ar[r]^{p_2} \ar[drr]_{f_2}& P \ar@{.>}[dr]|{\tilde{f}} & \\
      & & A  \\
    } \]
    would also commute (because $S$ is initial) but $\bar{f}$ is unique, hence $\bar{f} = \tilde{f}$.
  \end{proof}

@@

\begin{answer}
  \begin{itemize}
    \item[``$\Rightarrow$'']
      \emph{Counterexample:}
      Let $\cat{A} := \Set, E := \emptyset, X := \nat, Y := \mathbb{B}$.
      Define $f(n) := \text{even}(n)$ and $g(n) := \text{odd}(n)$. $i$ is the (empty) inclusion function.
      Then
      $\xymatrix@1{E \ar[r]^i &X \ar@<.5ex>[r]^{f}\ar@<-.5ex>[r]_g &Y}$
      is clearly a equalizer because no number is even and odd at the same time.
      Now let $A := \nat$, $f_1(n) := n$ and $f_2(n) := n+1$.
      Then the diagram
      \[ \xymatrix{
        A \ar[r]_{f_2} \ar[d]^{f_1} & Y \ar[d]_{g} \\
        X \ar[r]^f & Z
      } \]
      commutes because $\text{even}(n) \Leftrightarrow \text{odd}(n+1)$.
      But there exists no function $\bar{f} \from \nat \to \emptyset$ at all.
    \item[``$\Leftarrow$'']
      \begin{proof}
        Let
        \[ \xymatrix{
          E \ar[r]^i \ar[d]_i &
          X \ar[d]^g \\
          X \ar[r]_f &
          Y
        } \]
        be the pullback of the diagram
        $ \xymatrix{
          X \ar[r]^f & Y & X\ar[l]_g \\
        } $.
        We show that $\xymatrix@1{E \ar[r]^i &X \ar@<.5ex>[r]^{f} \ar@<-.5ex>[r]_g &Y}$ is the equalizer of $\xymatrix@1{X \ar@<.5ex>[r]^{f} \ar@<-.5ex>[r]_g &Y}$.
        First we note that the diagram $\xymatrix@1{E \ar[r]^i &X \ar@<.5ex>[r]^{f} \ar@<-.5ex>[r]_g &Y}$ is indeed a fork as it commutes by assumption.
        Let
        $ \xymatrix{
          A \ar[r]^f & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
        } $
        be a fork. Then
        \[ \xymatrix{
          A \ar[r]_{f} \ar[d]^{f} & X \ar[d]_{t} \\
          X \ar[r]^s & Y
        } \]
        commutes. Therefore exists a unique map $\bar{f}\from A \to P$ such that
        \[ \xymatrix{
          A \ar[drr]^{f} \ar[ddr]_{f} \ar@{.>}[dr]|{\bar{f}} & & \\
          & P \ar[r]_{i} \ar[d]^{i} & X \ar[d]_{t} \\
          & X \ar[r]^s & Y
        } \]
        commutes. We show that this $\bar{f}$ is the only map such that
        \[ \xymatrix{
          A \ar[rd]^f \ar@{.>}[dd]|{\bar{f}} & & \\
          & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y \\
          P \ar[ru]_i & &
        } \]
        commutes. First it is clear that this diagram commutes for $\bar{f}$. Now let $\tilde{f}$ be another map such that
        \[ \xymatrix{
          A \ar[rd]^f \ar@{.>}[dd]|{\tilde{f}} & & \\
          & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y \\
          P \ar[ru]_i & &
        } \]
        commutes. But then
        \[ \xymatrix{
          A \ar[drr]^{f} \ar[ddr]_{f} \ar@{.>}[dr]|{\tilde{f}} & & \\
          & P \ar[r]_{i} \ar[d]^{i} & X \ar[d]_{t} \\
          & X \ar[r]^s & Y
        } \]
        also commutes. By the assumption that $\bar{f}$ is unique we have $\bar{f} = \tilde{f}$. \qedhere
      \end{proof}
  \end{itemize}
\end{answer}

@@

\begin{answer}
  \begin{proof}
    We give names to the arrows and objects:
    \[ \xymatrix{
      A \ar[r]^h \ar[d]^j & B \ar[r]^i \ar[d]^k & C \ar[d]^l \\
      D \ar[r]^m & E \ar[r]^n & F
    } \]
    Now let the pullback square
    \[ \xymatrix{
      B \ar[r]^i \ar[d]^k & C \ar[d]^l \\
      E \ar[r]^n & F
    } \]
    be the pullback of $\xymatrix{E \ar[r]^n & F & C \ar[l]_l}$.
    We show both directions of the equivalence:
    \begin{itemize}
      \item[``$\Rightarrow$'']
        Let the pullback square
        \[ \xymatrix{
          A \ar[r]^{i \of h} \ar[d]^j & C \ar[d]^l \\
          D \ar[r]^{n \of m} & F
        } \]
        be the pullback of $\xymatrix{D \ar[r]^{n \of m} & F & C \ar[l]_l}$.
        Let
        \[ \xymatrix{
          Z \ar[r]^{f_1} \ar[d]^{f_2} & B \ar[d]^k \\
          D \ar[r]^{m} & E
        } \]
        be another pullback square. Now
        \[ \xymatrix{
          Z \ar[r]^{f_1} \ar[d]^{f_2} & B \ar[r]^{i} \ar[d]^k & C \ar[d]^l \\
          D \ar[r]^{m} & E \ar[r]^n & F
        } \]
        commutes. Now because the outer rectangle is a pullback there is a unique map $\bar{f} \from Z \to A$, such that
        \[ \xymatrix{
          Z \ar@/^/[drrr]^{i \of f_1}
            \ar@{.>}[dr]|{\bar{f}}
            \ar@/_/[ddr]_{f_2} & & \\
            & A \ar[r]_h \ar[d]^j & B \ar[r]_{i} & C \ar[d]_l \\
            & D \ar[r]^{m} & E \ar[r]^n & F
        } \]
        commutes. We show that this $\bar{f}$ is the unique map such that
        \[ \xymatrix{
          Z \ar@/^/[drr]^{f_1}
            \ar@{.>}[dr]|{\bar{f}}
            \ar@/_/[ddr]_{f_2} \\
          & A \ar[r]^h \ar[d]^j & B \ar[d]^k \\
          & D \ar[r]^m & E
        } \]
        commutes. We have to show $j \of \bar{f} = f_2$ and $h \of \bar{f} = f_1$. The first equatation holds by assumption.

>>>>

  Let $z$ be a greatest lower bound of the family $(x_i)_{i\in I}$. We show that $z$ is a product of $(x_i)_{i\in I}$.
  \begin{proof}
    We first have to define a family of maps $\Bigl(z \toby{p_i} x_i\Bigr)_{i \in I}$.
    This is trivial since we have $\forall i \in I: z \le x_i$.
    Now let $a \in A$ be an object and let $\Bigl(a \toby{f_i} x_i\Bigr)_{i \in I}$ be a family of maps from $a$.
    The existence of this maps means that $a$ is an upper bound of $(x_i)_{i\in I}$.
    Now by definition of least upper bound, $a \le z$, thus we have an arrow $\bar{f} \from a \to z$.
    All arrows are unique, thus $\bar{f}$ is the only map making the diagram commute. \qedhere
  \end{proof}
\end{answer}

@@

\begin{answer}
  \begin{proof}
    We first define the projection functions $p_1 \from V \oplus W \to V, p_2 \from V \oplus W \to W$:
    \begin{alignat*}{1}
      p_1(x,y) &:= x \\
      p_2(x,y) &:= y
    \end{alignat*}
    Clearly $p_1$ and $p_2$ are linear functions.
    Now let $A$ be a vector space and $f_1 \from A \to V, f_2 \from A \to W$ be linear functions.
    We define $\bar{f}(a) := (f_1(a), f_2(a))$. We clearly have
    \begin{alignat*}{2}
      p_1(\bar{f}(a)) &= p_1(f_1(a), f_2(a)) = f_1(a) \\
      p_2(\bar{f}(a)) &= p_2(f_1(a), f_2(a)) = f_2(a).
    \end{alignat*}
    Thus the diagram
    \[ \xymatrix{
        & A \ar[ldd]_{f_1} \ar@{.>}[d]|{\bar{f}\vphantom{\bar{\bar{f}}}} \ar[rdd]^{f_2} & \\
        & {V \oplus W} \ar[ld]^{p_1} \ar[rd]_{p_2} & \\
        V & & W
    } \]
    commutes. Now we have to show that $\bar{f}$ is the only map such that the above diagram commutes.
    Let $\tilde{f} \from A \to V \oplus W$ be a map such that $p_1 \of \tilde{f} = f_1 \land p_2 \of \tilde{f} = f_2$.
    \[
      \tilde{f}(a) = \bigl(p_1(\tilde{f}(a)), p_2(\tilde{f}(a))\bigr) = \bigl(f_1(a), f_2(A)\bigr) = \bar{f}(a)\qedhere
    \]
  \end{proof}
\end{answer}

@@

\begin{answer}
  \begin{proof}
    Let $i \from core(s-t) \to X$ be the inclusion function. Let
    $\xymatrix{
      A \ar[r]^f & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
    }$
    be a commuting diagram. Note that $f A \subseteq core(s-t)$.
    Thus we can define $\bar{f} \from A \to core(s-t)$ with $\bar{f}(a) := f(a)$.
    We see that $\forall a \in A: i(\bar{f}(a))=\bar{f}(a)=f(a)$, thus $i \of \bar{f} = f$.
    Let $\tilde{f} \from A \to core(s-t)$ be another map such that $i \of \tilde{f} = f$.
    Now $\tilde{f}(a) = i(\tilde{f}(a)) = i(\bar{f}(a)) = \bar{f}(a)$.
  \end{proof}
\end{answer}

@@

    \begin{itemize}
      \item[``$\Rightarrow$'']
        Let $s=t$. $1_X$ is an isomorphism and we show that the fork
        $\xymatrix{
          X \ar[r]^{1_X} & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
        }$
        is the equalizer. Let
        $\xymatrix{
          A \ar[r]^f & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
        }$
        be a fork.
        Clearly $\bar{f} := f$ is the only map $\bar{f} \from A \to X$ such that the diagram
        \[ \xymatrix{
          A \ar[rd]^f \ar@{.>}[dd]|{\bar{f}} & & \\
          & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y \\
          X \ar[ru]_{1_X} & &
        } \]
        commutes.
      \item[``$\Leftarrow$'']
        Let
        $\xymatrix{
          E \ar[r]^i & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
        }$
        be the equalizer and $i$ a isomorphism. Then by commutativity we get:
        \begin{alignat*}{4}
          && s \of i &= t \of i \\
          \Rightarrow  &\qquad& s \of i \of i^{-1} &= t \of i \of i^{-1} \\
          \Rightarrow  &      & s &= t
        \end{alignat*}\qedhere
    \end{itemize}
  \end{proof}
\end{answer}

@@

\begin{answer}
  \begin{proof}
    We show that $S := P$ is the coproduct of $X$ and $Y$ together with the coprojection functions $p_1$ and $p_2$.
    Let
    $ \xymatrix{
      X \ar[r]^{f_1} & A & Y \ar[l]_{f_2}
    } $
    be a diagram in $\cat{A}$.
    We have to show that there is a unique map $\bar{f}' \from P \to A$ such that
    \[ \xymatrix{
      X \ar[rdd]_{f_1}\ar[rd]^{p_1} & & Y \ar[ldd]^{f_2} \ar[ld]_{p_2} \\
      & P \ar@{.>}[d]|{\bar{f}'} & \\
      & A &
    } \]
    commutes. We know that the diagram
    \[ \xymatrix{
      Z \ar[r]_s \ar[d]^t & X \ar[d]_{f_1} \\
      Y \ar[r]^{f_2} & A
    } \]
    commutes because $Z$ is initial.
    Now because this square is then a pushout square there exists a unique map $\bar{f}\from P \to A$ such that
    \[ \xymatrix{
      Z \ar[r]_s \ar[d]^t & X \ar[d]_{p_1} \ar[ddr]^{f_1} & \\
      Y \ar[r]^{p_2} \ar[drr]_{f_2}& P \ar@{.>}[dr]|{\bar{f}} & \\
      & & A  \\
    } \]
    commutes. We see that we can choose $\bar{f}' := \bar{f}$.
    Suppose we have another $\tilde{f} \from P \to A$ such that
    \[ \xymatrix{
      X \ar[rdd]_{f_1}\ar[rd]^{p_1} & & Y \ar[ldd]^{f_2} \ar[ld]_{p_2} \\
      & P \ar@{.>}[d]|{\tilde{f}} & \\
      & A &
    } \]
    commutes. Then
    \[ \xymatrix{
      Z \ar[r]_s \ar[d]^t & X \ar[d]_{p_1} \ar[ddr]^{f_1} & \\
      Y \ar[r]^{p_2} \ar[drr]_{f_2}& P \ar@{.>}[dr]|{\tilde{f}} & \\
      & & A  \\
    } \]
    would also commute (because $Z$ is initial) but $\bar{f}$ is unique, hence $\bar{f} = \tilde{f}$.
  \end{proof}

@@

\begin{answer}
  \begin{itemize}
    \item[``$\Rightarrow$'']
      \emph{Counterexample:}
      Let $\cat{A} := \Set, E := \emptyset, X := \nat, Y := \mathbb{B}$.
      Define $f(n) := \text{even}(n)$ and $g(n) := \text{odd}(n)$. $i$ is the (empty) inclusion function.
      Then
      $\xymatrix@1{E \ar[r]^i &X \ar@<.5ex>[r]^{f}\ar@<-.5ex>[r]_g &Y}$
      is clearly the equalizer because no number is even and odd at the same time.
      Now let $A := \nat$, $f_1(n) := n$ and $f_2(n) := n+1$.
      Then the diagram
      \[ \xymatrix{
        A \ar[r]_{f_2} \ar[d]^{f_1} & Y \ar[d]_{g} \\
        X \ar[r]^f & Z
      } \]
      commutes because $\text{even}(n) \Leftrightarrow \text{odd}(n+1)$.
      But there exists no function $\bar{f} \from \nat \to \emptyset = E$ at all.
    \item[``$\Leftarrow$'']
      \begin{proof}
        Let
        \[ \xymatrix{
          E \ar[r]^i \ar[d]_i &
          X \ar[d]^g \\
          X \ar[r]_f &
          Y
        } \]
        be the pullback of the diagram
        $ \xymatrix{
          X \ar[r]^f & Y & X\ar[l]_g \\
        } $.
        We show that $\xymatrix@1{E \ar[r]^i &X \ar@<.5ex>[r]^{f} \ar@<-.5ex>[r]_g &Y}$ is the equalizer of $\xymatrix@1{X \ar@<.5ex>[r]^{f} \ar@<-.5ex>[r]_g &Y}$.
        First we note that the diagram $\xymatrix@1{E \ar[r]^i &X \ar@<.5ex>[r]^{f} \ar@<-.5ex>[r]_g &Y}$ is indeed a fork as it commutes by assumption.
        Let
        $ \xymatrix{
          A \ar[r]^f & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
        } $
        be a fork. Then
        \[ \xymatrix{
          A \ar[r]_{f} \ar[d]^{f} & X \ar[d]_{t} \\
          X \ar[r]^s & Y
        } \]
        commutes. Therefore there exists a unique map $\bar{f}\from A \to P$ such that
        \[ \xymatrix{
          A \ar[drr]^{f} \ar[ddr]_{f} \ar@{.>}[dr]|{\bar{f}} & & \\
          & P \ar[r]_{i} \ar[d]^{i} & X \ar[d]_{t} \\
          & X \ar[r]^s & Y
        } \]
        commutes. We show that this $\bar{f}$ is the only map such that
        \[ \xymatrix{
          A \ar[rd]^f \ar@{.>}[dd]|{\bar{f}} & & \\
          & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y \\
          P \ar[ru]_i & &
        } \]
        commutes. First it is clear that this diagram commutes for $\bar{f}$. Now let $\tilde{f}$ be another map such that
        \[ \xymatrix{
          A \ar[rd]^f \ar@{.>}[dd]|{\tilde{f}} & & \\
          & X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y \\
          P \ar[ru]_i & &
        } \]
        commutes. But then
        \[ \xymatrix{
          A \ar[drr]^{f} \ar[ddr]_{f} \ar@{.>}[dr]|{\tilde{f}} & & \\
          & P \ar[r]_{i} \ar[d]^{i} & X \ar[d]_{t} \\
          & X \ar[r]^s & Y
        } \]
        also commutes. By the assumption that $\bar{f}$ is unique we have $\bar{f} = \tilde{f}$. \qedhere
      \end{proof}
  \end{itemize}
\end{answer}

@@

\begin{answer}
  \begin{proof}
    We give names to the arrows and objects:
    \[ \xymatrix{
      A \ar[r]^h \ar[d]^j & B \ar[r]^i \ar[d]^k & C \ar[d]^l \\
      D \ar[r]^m & E \ar[r]^n & F
    } \]
    Now let the pullback square
    \[ \xymatrix{
      B \ar[r]^i \ar[d]^k & C \ar[d]^l \\
      E \ar[r]^n & F
    } \]
    be the pullback of $\xymatrix{E \ar[r]^n & F & C \ar[l]_l}$.
    We show both directions of the equivalence:
    \begin{itemize}
      \item[``$\Rightarrow$'']
        Let the pullback square
        \[ \xymatrix{
          A \ar[r]^{i \of h} \ar[d]^j & C \ar[d]^l \\
          D \ar[r]^{n \of m} & F
        } \]
        be the pullback of $\xymatrix{D \ar[r]^{n \of m} & F & C \ar[l]_l}$.
        Let
        \[ \xymatrix{
          Z \ar[r]^{f_1} \ar[d]^{f_2} & B \ar[d]^k \\
          D \ar[r]^{m} & E
        } \]
        be another pullback square for the left-hand square. Now
        \[ \xymatrix{
          Z \ar[r]^{f_1} \ar[d]^{f_2} & B \ar[r]^{i} \ar[d]^k & C \ar[d]^l \\
          D \ar[r]^{m} & E \ar[r]^n & F
        } \]
        commutes. Now because the outer rectangle is a pullback there is a unique map $\bar{f} \from Z \to A$, such that
        \[ \xymatrix{
          Z \ar@/^/[drrr]^{i \of f_1}
            \ar@{.>}[dr]|{\bar{f}}
            \ar@/_/[ddr]_{f_2} & & \\
            & A \ar[r]_h \ar[d]^j & B \ar[r]_{i} & C \ar[d]_l \\
            & D \ar[r]^{m} & E \ar[r]^n & F
        } \]
        commutes. We show that this $\bar{f}$ is the unique map such that
        \[ \xymatrix{
          Z \ar@/^/[drr]^{f_1}
            \ar@{.>}[dr]|{\bar{f}}
            \ar@/_/[ddr]_{f_2} \\
          & A \ar[r]^h \ar[d]^j & B \ar[d]^k \\
          & D \ar[r]^m & E
        } \]
        commutes. We have to show $j \of \bar{f} = f_2$ and $h \of \bar{f} = f_1$. The first equatation holds by assumption.
